An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Reduced the vertical size of the resample scatter plots, thereby eliminating blank pages. Closes Issue #16.

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=cdSpaghettiGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
cdData <- loadCDSpaghettiGraphData(energyType="none")
cdQData <- loadCDSpaghettiGraphData(energyType="Q")
cdData <- rbind(cdData, cdQData)
cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

@@

<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
                                mapping=aes(delta, sigma), 
                                facet_formula=countryAbbrev~nest, 
                                alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
cesSpaghettiGraph(data=spagData, level=1)
@

@@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

>>>>

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=cdSpaghettiGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
cdData <- loadCDSpaghettiGraphData(energyType="none")
cdQData <- loadCDSpaghettiGraphData(energyType="Q")
cdData <- rbind(cdData, cdQData)
cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

@@

<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelScatterGraphHeight, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
                    mapping=aes(delta, sigma), facet_formula=countryAbbrev~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
cesSpaghettiGraph(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

@@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
